Gaze model analysis

### 2023-09-24 stats/gazemodel.Rmd
incorporate Manuel's feedback

```{r arrange_plot}
setup_png <- ggdraw() + draw_image("../figures/gazemodel_logic_alpha.png", scale = 0.82)
ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_geometry_lines.png", scale = 0.95)

dev_plot <- readRDS(file = "../saves/gazemodel_dev_plot.rds")
model_vs_data_plot <- readRDS(file = "../saves/gazemodel_model_vs_data.rds")
u_plot <- readRDS("../saves/gazemodel_u_plot.rds")
corr_model_pred_plot <- readRDS("../saves/gazemodel_corr_model_pred_plot.rds")

gazemodel_plot <- ggarrange(
  setup_png,
  dev_plot, 
  NULL, 
  model_vs_data_plot,

  ulogic_png, 
  u_plot, 
  NULL, 
  corr_model_pred_plot,

  ncol = 4, 
  nrow = 2, 
  widths = c(9, 11, 1, 12), 
  labels = c("A", "B", "", "C", "D", "E", "", "F")
)

gazemodel_plot
saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white", device = cairo_pdf) 
# add cairo_pdf to enable greek symbols in pdf saving
```

>>>>

```{r arrange_plot}
dev_plot <- readRDS(file = "../saves/gazemodel_dev_plot.rds")
model_vs_data_plot <- readRDS(file = "../saves/gazemodel_model_vs_data.rds")
u_plot <- readRDS("../saves/gazemodel_u_plot.rds")
corr_model_pred_plot <- readRDS("../saves/gazemodel_corr_model_pred_plot.rds")

gazemodel_plot <- ggarrange(
  dev_plot, 
  NULL, 
  model_vs_data_plot,

  u_plot, 
  NULL, 
  corr_model_pred_plot,

  ncol = 3, 
  nrow = 2, 
  widths = c(11, 1, 12), 
  labels = c("A", "", "B", "C", "", "D")
)

gazemodel_plot
saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
ggsave("../figures/gazemodel_plot.png", width = 8, height = 5, scale = 1.3, bg = "white")
ggsave("../figures/gazemodel_plot.pdf", width = 8, height = 5, scale = 1.3, bg = "white", device = cairo_pdf) 
# add cairo_pdf to enable greek symbols in pdf saving
```
